FoRTE baseline

### 2019-04-15 analysis/paper/paper.Rmd
Add some notes from Longo ED2 GMD papers

@@

The Ecosystem Demography Model, version 2.X (ED2) [@medvigy_2009_mechanistic].

Summary of common features (can move into supplement if necessary):

@@

- Radiative transfer
  - Two-stream model (ED default)
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
  - Multiple scatter model
    - Based on @zhao_2005_multiple
- Crown model
  - Infinite (ED2 default)
    - Marginally taller cohorts completely shade out shorter ones
  - Finite
    - Cohorts have a finite crown area, so multiple cohorts have access to the same light level
    - Based on crown area allometries from @dietze_2008_changing
- Trait plasticity
  - None (ED default) -- Trait values are the same at all canopy heights and light levels
  - Plastic
    - V~cmax~(0) decreases with shading, and SLA increases with shading, based on @lloyd_2010_optimisation

@@

>>>>

[@longo_2019_ed1] provide a description of the most recent version of ED (2.2), and [@longo_2019_ed2] provide an evaluation.
However, these studies only consider the default configuration of ED2.
In fact, ED2 provides several alternative structures for some of its submodels.

@@

The Ecosystem Demography Model, version 2.2 (ED2).
Default configuration is described in [@longo_2019_ed1].
A brief summary of common features is as follows:

@@

- Radiative transfer
  - Two-stream model (ED default)
    - Same general approach as in CLM 4.5 [@clm45_note], but rather than solving for just two layers (sunlit and shaded), solve for each canopy layer.
    - Set up the two-stream equations for each layer as a linear system and solve the entire set of equations numerically
    - Similar to approaches used in other models: JULES [@mercado_2007_improving], ORCHIDEE-CAN [@naudts_2015_vertically], CLM(SPA) [@bonan_2014_modeling]
    - For details, see Supplements S9 and S10 in [@longo_2019_ed1].
  - Multiple scatter model
    - Based on @zhao_2005_multiple
- Crown model
  - Infinite (ED2 default)
    - Marginally taller cohorts completely shade out shorter ones
  - Finite
    - Cohorts have a finite crown area, so multiple cohorts have access to the same light level
    - Based on crown area allometries from @dietze_2008_changing
- Trait plasticity
  - None (ED default) -- Trait values are the same at all canopy heights and light levels
  - Plastic
    - V~cmax~(0) decreases with shading, and SLA increases with shading, based on @lloyd_2010_optimisation

@@

## Comparison against other studies

In two tropical sites, ED2 did a good job simulating observed top-of-canopy outgoing shortwave radiation, as well as radiation profiles [@longo_2019_ed2].
Completely closed canopy (i.e. no finite canopy radius) did not lead to an excessively dark understory; in fact, understory was slightly brighter than observed.
